\input shorts

{\title Logical romanticism}

{\date Saturday, 27 March 2021}

{\section Complex numbers}

\bigskip

\body

I haven't seen Roan for thirty six hours.  I've been through stages of
inanity to arrive at a reflection on an existence together.  Which
would be her point.  ``Not the easiest life, this one, together.''.  I
imagine.

I only know of the significance of intent.  The substance remains in
kindergarten.  ``A proper mess'', I said.  ``So special'', she
responded.  Our magic, not so magic bed.

If that's a relationship, kindergarten is a meet market.  However, by
generosity of intent the substance is relational due to significance.

I fear that if I gave her everything, we would have nothing.  That we
would collapse into the world, into the oceans of a subjective bed.
That the metaphysical partnership would not exist.  That a
subsistential metaphysics would be found.

Would be not found.  Lost to sense and reason we would be.

Free electron drift is the physical representation of what electrical
engineers call static electricity.  Basically, anything less than a
millivolt.  If a circuit has a microvolt potential, it would be
indistinguishable from nothing.

Like complex numbers, a relationship has the real physical part and
the imaginary metaphysical part.  The physical part is evident, and
the metaphysical part is lost to subsistence.

``To thine own self be true.''.  The sweet soul of self that lives at
the existential being is lost to the hyper-objectification and
hyper-rationalization common to the daze of subsistence.  The
indulgence of comfort and convenience.  The accomodation of inanity.

I lift myself up, out of those stages of missing to see my
misunderstanding.  To see my emotionalism.  My romanticism.  That
parisian psychoticism I know as energetic romanticism.

I do adore the physical accomodation of the metaphysical relationship.
And I do adore the metaphysical accomodation of the physical
relationship.

It works.  I keeps the mind out of bed, and the eyes in the head.  In
that magical, counterintuitive tantric practice that is experiential
existentialism.


{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
