\input shorts

{\title Experiential existentialism}

{\date Saturday, 18 April 2021}

{\section Conceptual learning}

\bigskip

Lying here with my eyes closed I can imagine that I'm here or there.
The conceptual trauma of learning broken.  There is no mystery.  I am
here.  And not there.  I know this.  And in this knowing I must
repair.

Rest.  Recall and not forget.  Remember to remember.  That I might
learn.  And in learning know.  That there is a difference, and that
the difference is not inconsequential.

Learning is like that.  The macroscopic actualization process feeds
into the microscopic actualization and realization process of self,
same, other, and society.  Of thought and language.  Of culture and
economy.  It needs to be broken.  By a school book.  By a school
house.  By the experience of macroscopic actualization different from
microscopic actualization.  That society and culture know these things
well.  That I must learn the things which are represented.  Because
there are many things without representation beyond the frontier of
self and person.  Without representation in language.  With
representation in culture in those redirections of illusion that serve
circumstance and condition.  That serve social, conceptual learning.

Learning in the conservation of self must reject the object, must
differentiate the object from its surroundings, relations, and
associations.  The process of objectification is like a muscle in this
way.  It must be exercised throughout the duration of life.  Across
the territories of experience.

The entanglements of learning make us a mess.  A soup of
unrealization.  The disrealization of self as learner, actor, and one
of many.  When soup of association is indistinguishable from.  When
there is no conceptual object.  When there is no lesson learned.

The conservation of self, same, other, and society recognizes
mutuality.  Recognizes that service is disentangling of person and
culture, of self and object.  That the recent history of thought in
culture has paved the earth over with control and capital as
manipulation and power.  That that abuse of the history of thought is
unrealized and self destructive.  Myopic and conceited.  Delusional.

Society in mutuality is conservative of life and liberty.  Of
independence and freedom.  Is independent of the myopia, conceit, and
delusion of dependence, imposition, indulgence, and indiscipline.  Is
independent of the physical and metaphysical ills that plague us.
That would mold, spoil, corrupt, and destroy our learning,
communication, and government.

When we disentangle society, environment, and economy we find that we
have separated ourselves from that abuse of economic capital which has
trained self to reward and compensation as survival by rent.  In
contrast, service as being and doing in society and world.  Balancing
the body budgets of energy and awareness against the worlds upon
worlds of socio-economic mutuality.

Is not each object of heart and mind, each object of the algebra of
breath and blood, an accumulation of steps?  Is not each object of
substance measured for significance in utility and durability to life
and living?

And do we not forget?  Do we not forget the terms of that algebra of
breath and blood?  Do we not forget the substance of life and the
significance of that substance?  That we breathe air?  That we eat
food?  That we have an impact yesterday, and a life tomorrow?  That it
is by reflection that we understand?  And that it is by understanding
that we comprehend?

{\tail John Pritchard, @syntelos [CC-BY-NC]}

\bye
